### 2023-03-14 main.tex
Update main.tex
check

    \Omega:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}^{V}
Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$ .\\

@@

\mathcal{L}_{x,y}f(n)=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(n-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(n)\right]

@@

    \mathcal{L}_{x}f(n)=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(n+\delta_{k}^{x}-\delta_{l}^{x})-f(n)\right]

@@

where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
\end{equation}
By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
\begin{equation}
\label{duality-function-good}
    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
\end{equation}
We denote by $D_{x}$ the site part. This is defined as 
\begin{equation}
    D_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}
    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
\end{equation}
that implies 
\begin{equation}
    \exp{(E^{x})}=I+E^{x}
\end{equation}
and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
\begin{equation}
    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
\begin{equation}\label{dualityMatrix}
D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
\end{equation}
On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph. On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$. This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites. Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
\subsection{Proof of the duality relation}\label{subsectionDualityProof}
To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{duality-function-good} we shall show that 
\begin{equation}
    H^{T}D=D\widetilde{H}
\end{equation}
Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
\begin{equation}\label{edgeDualRealtion}
    H_{x,y}^{T}D=DH_{x,y}\qquad \forall x,y\in \mathcal{E}
\end{equation}
and for the site Hamiltonians 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We will prove these two statements seprately in the following.

>>>>

    \Omega:=\Omega_{x}^{V}
\Omega_{x}:=\left\{(n_{1},\ldots,n_{N})\in\mathbb{N}_0^{N}\;:\; \sum_{k=1}^{N}n_{k}=\twoj\right\}
Moreover, we denote a particle configuration as $\mathbf{n}\in \Omega$, where $\mathbf{n}=(n_{k}^{x})_{x\in V,\,k\in\{1,\ldots,N\}}$  and we denote the site occupation vector as $n^{x}=(n_{1}^{x},\ldots,n_{N}^{x})$, for all $x\in V$.\\

@@

\mathcal{L}_{x,y}f(\bm{n})=\sum_{k,l=1}^{N}n_{k}^{x}n_{l}^{y}\left[f(\bm{n}-\delta_{x}^{k}+\delta_{l}^{x}+\delta_{k}^{y}-\delta_{l}^{y})-f(\bm{n})\right]

@@

    \mathcal{L}_{x}f(\bm{n})=\sum_{k,l=1}^{N}\alpha_{k}^{x}n_{l}^{x}\left[f(\bm{n}+\delta_{k}^{x}-\delta_{l}^{x})-f(\bm{n})\right]

@@

where $H_{x,y}$ is the one defined in \eqref{edgeHamiltonian}, while 
\begin{equation}\label{siteDualHamiltonian}
    \widetilde{H}_{x}=\sum_{i=1}^{N}\alpha_{i}^{x}\sum_{k=2}^{N}\left((a^{\dagger})_{k}^{\widetilde{x}}\,E_{1k}^{x}-E_{kk}^{x}\right)
\end{equation}
By introducing the action of a bosonic creation operator $a^{\dagger}|q\rangle=|q+1\rangle$ on a generic vector $|q\rangle$ with $q\in \mathbb{N}_{0}$, we define in \eqref{siteDualHamiltonian} 
$(a^{\dagger})_{k}^{\widetilde{x}}$ as a copy of $a^{\dagger}$ acting on the extra-site $\widetilde{x}$ and on the occupation of the species $k\in\{2,\ldots,N\}$. \\
The Hamiltonians \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} are dual with respect to the duality matrix $D$ defined as 
\begin{equation}
\label{duality-function-good}
    D=\bigotimes_{x\in V}\left(D_{x}\otimes D_{\widetilde{x}}\right)
\end{equation}
We denote by $D_{x}$ the site part. This is defined as 
\begin{equation}
    D_{x}=R_{x}\exp{(E^{x})}
\end{equation}
with 
\begin{equation}
    E^{x}=\sum_{k=2}^{N}E_{k1}^{x}
\end{equation}
that implies 
\begin{equation}
    \exp{(E^{x})}=I+E^{x}
\end{equation}
and where $R_{x}$ is the diagonal matrix with elements (up to a finite constant) the inverse of the masses of the reversible measure \eqref{reversibleMeasure}, i.e. 
\begin{equation}
    R_{x}=\sum_{n\in\chi}\frac{\prod_{k=1}^{N}n_{k}^{x}}{\nu!}|n_{1}^{x},\ldots,n_{N}^{x}\rangle\langle n_{1}^{x},\ldots,n_{N}^{x}|
\end{equation}
where, for all $x\in V$, we call $\chi=\{(n_{k}^{x})_{k\in\{1,\ldots,N\}}\in \mathbb{N}_{0}\,:\, \sum_{k=1}^{N}n_{k}^{x}=\nu\}$ the simplex.\\ 
We denote by $D_{\widetilde{x}}$ the extra-site part. It is defined as
\begin{equation}\label{dualityMatrix}
D_{\widetilde{x}}=\sum_{m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}=0}^{\infty}\prod_{k=2}^{N}\left(\frac{\alpha_{k}^{x}}{\sum_{i=1}^{N}\alpha_{i}^{x}}\right)\langle m_{2}^{\widetilde{x}},\ldots,m_{N}^{\widetilde{x}}|
\end{equation}
On one hand, the edge part of the dual Hamiltonian \eqref{DualHamiltonian} is a copy of \eqref{edgeHamiltonian}, therefore it performs the stirring dynamic on the graph. On the other hand, the site dual Hamiltonian \eqref{siteDualHamiltonian} replaces a particle of any type $k\in\{2,\ldots,N\}$ at site $x$ with a particle of type $1$ and creates a particle of the same type $k$ at the extra-site $\widetilde{x}$. This means that, eventually, only particles of type $1$ remain in the graph while all other types are absorbed by the extra-sites. Thinking about the type $1$ as the hole  the graph is eventually emptied, similarly to what proved in the SEP(2j)\cite{carinci2013duality}.
\subsection{Proof of the duality relation}\label{subsectionDualityProof}
To prove the duality relation between \eqref{OriginalHamiltonian} and \eqref{DualHamiltonian} with the duality matrix \eqref{duality-function-good} we shall show that 
\begin{equation}
    H^{T}D=D\widetilde{H}
\end{equation}
Since the duality matrix is a tensor product over the sites $x\in V$ it is enough to prove that for the edge Hamiltonians
\begin{equation}\label{edgeDualRealtion}
    H_{x,y}^{T}D=DH_{x,y}\qquad \forall (x,y)\in \mathcal{E}
\end{equation}
and for the site Hamiltonians 
\begin{equation}\label{siteDualRelation}
    H_{x}^{T}D=D\widetilde{H}_{x}\qquad \forall x\in V.
\end{equation}
We will prove these two statements separately in the following.
